Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-13 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
related work 初稿完成

%START: added by zhbli
\usepackage{subfigure}  % show sub-figure
\usepackage{algorithm}  % for algrithm
\usepackage{algorithmic}  % for algrithm
\usepackage{multirow}  % for multirow command used in the table
\usepackage{amsfonts}  % for mathbb
\usepackage{color,xcolor}  % 用于改变字体颜色
\usepackage{amssymb}  % 用于打对号
\usepackage{amsfonts}  % 用于 mathbb
\newcommand{\eg}{e.g.}
\newcommand{\ie}{i.e.}
%\usepackage{float}  % 如果你确实需要把图片放在当前位置，不容改变，可以用float宏包的[H]选项。
%\usepackage[section]{placeins}  % 如果希望避免浮动体跨过 \section，可以使用 placeins 宏包。
%END: added by zhibi

@@

\title{Video-Agnostic Perturbation: Efficient Targeted Attacks \\ for Siamese Visual Tracking}

@@

Recently, the robustness of Siamese trackers have recently attracted a lot of attention \cite{TemporallyTransferablePerturbations} \cite{efficient} \cite{guo2020spark}. Despite the impressive performance of Siamese architectures on challenging visual object tracking task, these trackers were shown to be highly vulnerable to perturbations.
\cite{TemporallyTransferablePerturbations} \textcolor{black}{propose a framework to generate a single temporally transferable adversarial perturbation from the object template image only. This perturbation can then be added to every search image to adversarially attack the subsequent video frames.}
\cite{efficient} \textcolor{black}{present an end-to-end network FAN (Fast Attack Network) that uses a novel drift loss combined with the embedded feature loss to attack the Siamese network based trackers.}
\cite{guo2020spark} \textcolor{black}{propose the spatial-aware online incremental attack (a.k.a. SPARK) that performs spatial-temporal sparse incremental perturbations online and makes the adversarial attack less perceptible.}

@@

Visual object tracking is a fundamental problem in computer vision, estimating the position of a template cropped from the first frame of a video in each of the subsequent video frames.
The state-of-the-art trackers can be roughly summarized to three categories, including correlation filter-based, classification \& updating-based and Siamese network-based trackers.
Recently, Siamese networks \cite{ATOM} \cite{SiamFC} have demonstrated a significant improvement in object tracking performances. Siamese trackers formulate the visual object tracking problem as learning cross-correlation similarities between a target template and a search region. Tracking is then performed by finding the target object from the search image region by computing the highest visual similarity.
In particular, SiamRPN consists of Siamese subnetwork for feature extraction and region proposal subnetwork including the classification branch and regression branch. In the inference phase, the proposed framework is formulated as a local one-shot detection task.
SiamRPN++ breaks the restriction of strict translation invariance through a simple yet effective spatial aware sampling strategy and successfully train a ResNet-driven Siamese tracker with significant performance gain.
SiamFC++ \cite{SiamFC++} is designed by introducing both classification and target state estimation branch, classification score without ambiguity, tracking without prior knowledge, and estimation quality score.
In our experiments, we will focus on the SiamFC++ tracker due to its popularity in real-world applications. Nevertheless, we will study the transferability of our generated adversarial attacks to other trackers.

@@

The imperceptible perturbations most commonly modify each pixel by on a small amount and can be found using a number of optimisation strategies such as L-BFGS \cite{intriguing}, Fast Gradient Sign Method (FGSM) \cite{FGSM}, and PGD \cite{PGD}.
Different from the imperceptible perturbation, the adversarial patch is extremely salient to a neural network. This patch can be placed anywhere into the input image, and causes the network to misbehave.
To the best of our knowledge, we are the first to attacker object trackers utilizing both the imperceptible perturbation and the adversarial patch together, which are jointly trained in an end-to-end manner.
Note that our patch works in the network domain instead of the image domain. In the network-domain case, the noise is allowed to take any value and is not restricted to the dynamic range of images, while in the image domain case the noise is kept to the dynamic-range of images.

@@

In the case of non-universal attack, the perturbations are specifically crafted of each data point independently, while the universal attack seeks a single perturbation that fools the network on most data points.
There are some papers try to find the universal perturbations. In \cite{moosavi2017universal}, they propose this idea.

@@

Recently, there are several explorations of the adversarial attacks on the visual object tracking task. For example, PAT generated physical adversarial textures visa white-box attack to let the tracker lock on the texture when a tracked object moves in front of it. However, PAT validates its method by attacking a light deep regression tracker, i.e., GOTURN that has low tracking accuracy on modern benchmarks. In this paper, we aim to attack the state-of-the-art trackers based on the Siamese networks.
RTAA \cite{RTAA} takes temporal motion into consideration when generating lightweight perturbations over the estimated tracking results frame-by-frame. However, RTAA only performs the untargeted attack for tarckers, which causes the adversarial trajectory to deviate from the original trajectory of an object. In this paper, we focus on the more challenging targeted attack for object tracking.
SPARK \cite{SPARK} computes incremental perturbations by using information from the past frames to perform targeted attack against Siamese trackers. However, SPARK needs to generate the adversarial example for every search image in a video, which is time-consuming and ill-suited to attack an online visual tracking system in real time. In this paper, we propose universal perturbations which allow perturbing a novel video to come at no additional cost except the mere addition and pasting operations.

>>>>

%START: added by zhbli
\usepackage{subfigure}  % show sub-figure
\usepackage{algorithm}  % for algrithm
\usepackage{algorithmic}  % for algrithm
\usepackage{multirow}  % for multirow command used in the table
\usepackage{amsfonts}  % for mathbb
\usepackage{color,xcolor}  % 用于改变字体颜色
\usepackage{amssymb}  % 用于打对号
\usepackage{amsfonts}  % 用于 mathbb
%\usepackage{cite}  % 用于引用多篇文献
\newcommand{\eg}{e.g.}
\newcommand{\ie}{i.e.}
%\usepackage{float}  % 如果你确实需要把图片放在当前位置，不容改变，可以用float宏包的[H]选项。
%\usepackage[section]{placeins}  % 如果希望避免浮动体跨过 \section，可以使用 placeins 宏包。
%END: added by zhibi

@@

\title{Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking}

@@

Recently, the robustness of Siamese trackers have recently attracted a lot of attention \cite{TemporallyTransferablePerturbations} \cite{efficient} \cite{SPARK}. Despite the impressive performance of Siamese architectures on challenging visual object tracking task, these trackers were shown to be highly vulnerable to perturbations.
\cite{TemporallyTransferablePerturbations} \textcolor{black}{propose a framework to generate a single temporally transferable adversarial perturbation from the object template image only. This perturbation can then be added to every search image to adversarially attack the subsequent video frames.}
\cite{efficient} \textcolor{black}{present an end-to-end network FAN (Fast Attack Network) that uses a novel drift loss combined with the embedded feature loss to attack the Siamese network based trackers.}
\cite{SPARK} \textcolor{black}{propose the spatial-aware online incremental attack (a.k.a. SPARK) that performs spatial-temporal sparse incremental perturbations online and makes the adversarial attack less perceptible.}

@@

Visual object tracking is a fundamental problem in computer vision, estimating the position of a template cropped from the first frame of a video in each of the subsequent video frames.
The state-of-the-art trackers can be roughly summarized to three categories, including correlation filter-based, classification \& updating-based and Siamese network-based trackers.
Recently, Siamese networks \cite{SiamRPN} \cite{SiamRPN++} have demonstrated a significant improvement in object tracking performances. Siamese trackers formulate the visual object tracking problem as learning cross-correlation similarities between a target template and a search region. Tracking is then performed by finding the target object from the search image region by computing the highest visual similarity.
In particular, SiamRPN \cite{SiamRPN} consists of Siamese subnetwork for feature extraction and region proposal subnetwork including the classification branch and regression branch. In the inference phase, the proposed framework is formulated as a local one-shot detection task.
SiamRPN++ \cite{SiamRPN++} breaks the restriction of strict translation invariance through a simple yet effective spatial aware sampling strategy and successfully train a ResNet-driven Siamese tracker with significant performance gain.
SiamFC++ \cite{SiamFC++} is designed by introducing both classification and target state estimation branch, classification score without ambiguity, tracking without prior knowledge, and estimation quality score.
In our experiments, we will focus on the SiamFC++ tracker due to its popularity in real-world applications. Nevertheless, we will study the transferability of our generated adversarial attacks to other trackers.

@@

The imperceptible perturbations most commonly modify each pixel by on a small amount and can be found using a number of optimisation strategies such as L-BFGS \cite{intriguing}, Fast Gradient Sign Method (FGSM) \cite{FGSM}, and PGD \cite{PGD}.
Different from the imperceptible perturbation, the adversarial patch is extremely salient to a neural network. The adversarial patch can be placed anywhere into the input image, and causes the network to misbehave.
To the best of our knowledge, we are the first to attack object trackers utilizing both the imperceptible perturbation and the adversarial patch together, which are jointly trained in an end-to-end manner.
Note that our adversarial patch works in the network domain instead of the image domain. In the network-domain case, the noise is allowed to take any value and is not restricted to the dynamic range of images, while in the image domain case the noise is kept to the dynamic-range of images.

@@

In the case of non-universal attack, the perturbations are specifically crafted of each data point independently, while the universal attack seeks a single perturbation that fools the network on most data points.
In this paper, we perform the universal attack for Siamese tracker.

@@

Recently, there are several explorations of the adversarial attacks on the visual object tracking task. For example, PAT \cite{PAT} generates physical adversarial textures visa white-box attack to let the tracker lock on the texture when a tracked object moves in front of it. However, PAT validates its method by attacking a light deep regression tracker, i.e., GOTURN \cite{GOTURN} that has low tracking accuracy on modern benchmarks. In this paper, we aim to attack the state-of-the-art trackers based on the Siamese networks.
RTAA \cite{RTAA} takes temporal motion into consideration when generating lightweight perturbations over the estimated tracking results frame-by-frame. However, RTAA only performs the untargeted attack for tarckers, which causes the adversarial trajectory to deviate from the original trajectory of an object. In this paper, we focus on the more challenging targeted attack for object tracking.
SPARK \cite{SPARK} computes incremental perturbations by using information from the past frames to perform targeted attack against Siamese trackers. However, SPARK needs to generate the adversarial example for every search image in a video, which is time-consuming and ill-suited to attack an online visual tracking system in real time. In this paper, we propose universal perturbations which allow perturbing a novel video to come at no additional cost except the mere addition and pasting operations.
